Energy and the CES production function

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better formatting for tables. Rearrange paper.

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
                                                                        data = historicalData[[country]], 
                                                                        nest=c(1,2), digits = 10)
      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest, digits = 10)
        })
    }      
  }
  # Save models to disk.
  saveRDS(models, file=fileNameCDCES)
}
# Put all exponential model coefficients into a data frame
AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
  # Parse the id to find details of this model
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = NA,
                    energy = "Without energy", 
                    model = "exp", 
                    nest = NA,
                    CSP = "Reject CSP"))
  res <- cbind(res, naturalCoef(modExp))
  # Now caluculate mean squared error (sse) for each model.
  sse <- sum(resid(modExp)^2)
  res <- cbind(res, list(sse=sse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

@@

Both historical GDP and fitted GDP are shown in 
Figures~\ref{fig:Graphs_CESkle-fitted}--\ref{fig:Graphs_CESekl-fitted}.
%
<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
fittedGraphData_kle <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
fittedGraphNoCSP(fittedGraphData_kle)
@
%
<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
fittedGraphNoCSP(fittedGraphData_lek)
@
%
<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
fittedGraphNoCSP(fittedGraphData_ekl)
@

@@

<<ResidualPlotFunction>>=

residualPlot <- function(data, withEnergyShape = 0){
  ggplot() +
    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
    scale_shape_manual(values=c(1, withEnergyShape)) +
    scale_size_manual(values=c(4,4)) +
    facet_grid(Country ~ flavor) +
    # geom_hline(aes(yintercept = 0), colour="gray50", size=0.1) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xlab("") +
    ylab("r") + 
    xy_theme() +
    theme(legend.title=element_blank())
}

Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
show fitting residuals for all CES models.
%
<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
             withEnergyShape = 0) # square
@
%
<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
             withEnergyShape = 3) # plus
@
%
<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
             withEnergyShape = 4) # times
@

@@

Table~\ref{tab:CES_sr_gof} shows 
the Solow residual~($\lambda$) and
goodness of fit~($sse$)
for all modeling decisions.
%
<<CES_sr_gof, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
           select(Country, model, flavor, energy, nest, CSP, scale, lambda, sse),
         caption="$\\theta$, Solow residual, and $sse$ for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
We can evaluate the effect of modeling decisions on 
goodness of fit and Solow residual by
calculating values relative to the reference model.
To do so, we define 
$\Delta \lambda$ and $\Delta sse$, where
%
\begin{equation} \label{eq:delta_lambda}
  \Delta \lambda \equiv \lambda - \lambda_{ref}
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_sse}
  \Delta sse \equiv sse - sse_{ref},
\end{equation}
%
with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
of the Solow residual and $sse$ for the reference model, respectively.
On a percentage basis,
%
\begin{equation} \label{eq:delta_lambda_perc}
  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_sse_perc}
  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
\end{equation}

@@

@@

%------------------------------
\subsubsection{Rejecting (or adhering to) the cost share theorem} 
\label{sec:gfsr_CSP}
%------------------------------

%------------------------------
\subsubsection{Quality-adjusting (or not) factors of production} 
\label{sec:gfsr_fop}
%------------------------------

%------------------------------
\subsubsection{Including energy (or not)} 
\label{sec:gfsr_energy}
%------------------------------

%------------------------------
\subsubsection{CES nesting} 
\label{sec:gfsr_nesting}
%------------------------------

Table~\ref{tab:CES_alpha} shows 
the factor shares~($\alpha_i$ values) for all CES modeling decisions.
%
<<CES_alpha, results="asis">>=
data_CES_alpha <- filter(AllCoeffs, model=="CES" | model=="exp") %>% 
  select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
data_CES_alpha <- plyr::rename(data_CES_alpha, c("alpha_1" = "$\\alpha_1$",
                                                 "alpha_2" = "$\\alpha_2$",
                                                 "alpha_3" = "$\\alpha_3$"))
myXTable(data_CES_alpha,
         caption="Factor shares~($\\alpha$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
show factor shares ($\alpha$ values) for CES models for
Portugal and the UK, respectively.
See Table~\ref{tab:CES_abg_equations} for details on the calculation
of factor shares from fitted values of $\delta_1$ and $\delta$.
%
<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
  # Change nest to a nicer-looking nest string
  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
  # Add a label column
  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
  # Add row numbers to the label column
  bar_chart_data$label <- paste(paste0(1:length(bar_chart_data$label), ". "), bar_chart_data$label)
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  bar_chart_data <- melt(bar_chart_data, 
                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
                         value.name = "value", 
                         variable.name = "variable")
  bar_chart_data$variable <- plyr::mapvalues(bar_chart_data$variable, 
                                       from=c("alpha_1", "alpha_2", "alpha_3"), 
                                       to=c("alpha_k", "alpha_l", "alpha_e"))

@@

%------------------------------
\subsubsection{Rejecting (or adhering to) the cost share theorem} 
\label{sec:fs_CSP}
%------------------------------

%------------------------------
\subsubsection{Quality-adjusting (or not) factors of production} 
\label{sec:fs_fop}
%------------------------------

%------------------------------
\subsubsection{Including energy (or not)} 
\label{sec:fs_energy}
%------------------------------

%------------------------------
\subsubsection{CES nesting} 
\label{sec:fs_nesting}
%------------------------------

%++++++++++++++++++++++++++++++
\subsection{Factor substitutability} 
\label{sec:substitutability}
%++++++++++++++++++++++++++++++

Table~\ref{tab:CES_sigma} shows 
substitutability parameters~($\sigma_i$ values) 
for all CES modeling decisions.

**** Note: At the present time, Table~\ref{tab:CES_sigma}
requires a LOT of effort to interpret, 
because $\sigma_1$ and $\sigma$ have different meanings
for each nesting.
I'm planning to change the table to make interpretation easier. ---MKH ****

**** Is there a graph we want to make here? ---MKH ****
%
<<CES_sigma_table_data>>=
sigma_data <- filter(AllCoeffs, model=="CES") 
sigma_data <- plyr::rename(sigma_data, c("model" = "Model", "flavor" = "Type", "energy" = "Energy", "nest" = "Nest"))
@

<<CES_sigma, results="asis">>=
data_CES_sigma_raw <- sigma_data %>% select(Country, Model, Type, Energy, Nest, CSP, sigma_1, sigma)
data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
                                                         "sigma_1" = "$\\sigma_1$"))
myXTable(data_CES_sigma_raw,
         caption="Factor substitution~($\\sigma$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Factor substitution~($\\sigma$) for CES models. Inner nests.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Factor substitution~($\\sigma$) for CES models. Outer nests.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

%------------------------------
\subsubsection{Rejecting (or adhering to) the cost share theorem} 
\label{sec:sigma_CSP}
%------------------------------

%------------------------------
\subsubsection{Quality-adjusting (or not) factors of production} 
\label{sec:sigma_fop}
%------------------------------

%------------------------------
\subsubsection{Including energy (or not)} 
\label{sec:sigma_energy}
%------------------------------

%------------------------------
\subsubsection{CES nesting} 
\label{sec:sigma_nesting}
%------------------------------

@@

@@

This appendix contains correlograms for all models.

@@

<<Correlograms_Exp, echo=FALSE, message=FALSE>>=
leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_CSP, echo=FALSE, message=FALSE>>=
leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_noCSP, echo=FALSE, message=FALSE>>=
leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<stat_details_table, results="asis">>=
texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
       dcolumn = TRUE, 
       booktabs = TRUE, 
       use.packages = FALSE, 
       label=paste0("tab:", opts_current$get("label")), 
       caption = "Example output from \\texttt{texreg}.",
       caption.above = TRUE, 
       digits = 6,
       fontsize = "tiny",
       float.pos = "hb")
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cobb-Douglas Graveyard} 
\label{sec:cd_results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
                                                                        data = historicalData[[country]], 
                                                                        nest=c(1,2), digits = 10)
      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest, digits = 10)
        })
    }      
  }
  # Save models to disk.
  saveRDS(models, file=fileNameCDCES)
}
# Put all exponential model coefficients into a data frame
AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
  # Parse the id to find details of this model
  id_list <- strsplit(id, split = "[.]")[[1]]
  res <- rbind(list(Country = id_list[[1]], 
                    flavor = NA,
                    energy = "Without energy", 
                    model = "exp", 
                    nest = NA,
                    CSP = NA))
  res <- cbind(res, naturalCoef(modExp))
  # Now caluculate mean squared error (sse) for each model.
  sse <- sum(resid(modExp)^2)
  res <- cbind(res, list(sse=sse))
  return(res)
}) %>% do.call(plyr::rbind.fill, .)

@@

@@

@@

%
We can evaluate the effect of modeling decisions on 
goodness of fit and Solow residual by
calculating values relative to the reference model.
To do so, we define 
$\Delta \lambda$ and $\Delta sse$, where
%
\begin{equation} \label{eq:delta_lambda}
  \Delta \lambda \equiv \lambda - \lambda_{ref}
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_sse}
  \Delta sse \equiv sse - sse_{ref},
\end{equation}
%
with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
of the Solow residual and $sse$ for the reference model, respectively.
On a percentage basis,
%
\begin{equation} \label{eq:delta_lambda_perc}
  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
\end{equation}
%
and
%
\begin{equation} \label{eq:delta_sse_perc}
  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Graphs for paper} 
\label{sec:graphs_for_paper}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Both historical GDP and fitted GDP are shown in 
Figures~\ref{fig:Graphs_CESkle-fitted}--\ref{fig:Graphs_CESekl-fitted}.
%
<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
fittedGraphData_kle <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
fittedGraphNoCSP(fittedGraphData_kle)
@

<<ResidualPlotFunction>>=
residualPlot <- function(data, withEnergyShape = 0){
  ggplot() +
    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
    scale_shape_manual(values=c(1, withEnergyShape)) +
    scale_size_manual(values=c(4,4)) +
    facet_grid(Country ~ flavor) +
    # geom_hline(aes(yintercept = 0), colour="gray50", size=0.1) +
    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xlab("") +
    ylab("r") + 
    xy_theme() +
    theme(legend.title=element_blank())
}

Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
show fitting residuals for all CES models.
%
<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
             withEnergyShape = 0) # square
@
%

@@

%
Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
show factor shares ($\alpha$ values) for CES models for
Portugal and the UK, respectively.
See Table~\ref{tab:CES_abg_equations} for details on the calculation
of factor shares from fitted values of $\delta_1$ and $\delta$.
%
<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
  # Change nest to a nicer-looking nest string
  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
  # Add a label column
  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
  # Add row numbers to the label column
  bar_chart_data$label <- paste(paste0(1:length(bar_chart_data$label), ". "), bar_chart_data$label)
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  bar_chart_data <- melt(bar_chart_data, 
                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
                         value.name = "value", 
                         variable.name = "variable")
  bar_chart_data$variable <- plyr::mapvalues(bar_chart_data$variable, 
                                       from=c("alpha_1", "alpha_2", "alpha_3"), 
                                       to=c("alpha_k", "alpha_l", "alpha_e"))

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tables for paper} 
\label{sec:tables_for_paper}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Table~\ref{tab:CES_sr_gof} shows estimated values of
the scale parameter~($\theta$),
the Solow residual~($\lambda$), and
goodness of fit~($sse$)
for all modeling choices.

<<Table_data>>=
table_data <- AllCoeffs 
table_data <- plyr::rename(table_data, c("model" = "Model", 
                                         "energy" = "Energy", 
                                         "nest" = "Nest"))
table_data$Nest <- plyr::mapvalues(table_data$Nest,
                                   from=c("kl", "kle", "lek", "ekl"),
                                   to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$"))
table_data$CSP <- plyr::mapvalues(table_data$CSP, 
                                  from=c("Adhere to CSP", "Reject CSP"), 
                                  to=c("Adhere", "Reject"))
table_data$Energy <- plyr::mapvalues(table_data$Energy, 
                                     from=c("Without energy", "With energy"), 
                                     to=c("Without", "With"))
table_data$model <- plyr::mapvalues(table_data$model, 
                                    from=c("exp"), 
                                    to=c("Ref."))
@

<<CES_sr_gof, results="asis">>=
data_CES_SR_gof <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, flavor, Energy, Nest, CSP, scale, lambda, sse)
data_CES_SR_gof <- plyr::rename(data_CES_SR_gof, c("flavor" = "Factors of prod.",
                                                   "scale" = "$\\theta$",
                                                   "lambda" = "$\\lambda$"))
myXTable(data_CES_SR_gof,
         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

Table~\ref{tab:CES_alpha} shows 
output elasticities~($\alpha$) for all modeling choices.

<<CES_alpha, results="asis">>=
data_CES_alpha <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
  select(Country, Model, flavor, Energy, Nest, CSP, alpha_1, alpha_2, alpha_3)
data_CES_alpha <- plyr::rename(data_CES_alpha, c("flavor" = "Factors of prod.",
                                                 "alpha_1" = "$\\alpha_k$",
                                                 "alpha_2" = "$\\alpha_l$",
                                                 "alpha_3" = "$\\alpha_e$"))
myXTable(data_CES_alpha,
         caption="Output elasticities~($\\alpha$) for all models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

<<CES_sigma_table_data>>=
# This chunk does some preliminary processing
@

Table~\ref{tab:CES_sigma_nest_aware_inner} shows elasticity of substitution~($\sigma$)
for inner nests.
Note that the row with 
``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
is, in fact, a boundary model that does not include energy.
As such, the only knowable elasticity is $\sigma_{kl}$.

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
                                                     "sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Factor substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

Table~\ref{tab:CES_sigma_nest_aware_outer} shows elasticity of substitution~($\sigma$)
for outer nests.
Rows with the $kl$ nesting are blank, because they have no outer nest.
The row with
``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
has no values for $\sigma$, because it has no outer nest, being a boundary model
that includes only~$k$ and~$l$.

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
                                                     "sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Factor substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

This appendix contains correlograms for all models.
But, they are not included for now.

@@

<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE>>=
leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE>>=
leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE>>=
leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
  acf(resid(model), main=name)
})
@

@@

This information is not included at present.

<<stat_details_table, results="asis", include=FALSE>>=
texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
       dcolumn = TRUE, 
       booktabs = TRUE, 
       use.packages = FALSE, 
       label=paste0("tab:", opts_current$get("label")), 
       caption = "Example output from \\texttt{texreg}.",
       caption.above = TRUE, 
       digits = 6,
       fontsize = "tiny",
       float.pos = "hb")
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pre-econometrics graph} 
\label{sec:pre-econometric_graph}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cobb-Douglas Graveyard} 
\label{sec:cd_graveyard}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CES Graveyard} 
\label{sec:ces_graveyard}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here is a table of the raw CES coefficient values. 
This table is not used in the paper, so I'm putting it in 
<<CES_sigma, results="asis">>=
data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
                                                         "sigma_1" = "$\\sigma_1$"))
data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
                                         from=c("Adhere to CSP", "Reject CSP"), 
                                         to=c("Adhere", "Reject"))
data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
                                         from=c("Without energy", "With energy"), 
                                         to=c("Without", "With"))

myXTable(data_CES_sigma_raw,
         caption="Factor substitution~($\\sigma$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
             withEnergyShape = 3) # plus
@
%
<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
             withEnergyShape = 4) # times
@

%
<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
fittedGraphNoCSP(fittedGraphData_lek)
@
%
<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
fittedGraphNoCSP(fittedGraphData_ekl)
@
